Visualization of the Riemann-Liouville Fractional Integral

### 2019-05-29 fractional/CMJ style files/article-template.tex
newest version

\title{Visualization of [fulle name] Fractional Integrals}
\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
%\author{ }

@@

To conclude this section, a fractional integral of order $\alpha$ and extent $t$ can be interpreted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
shape is determined by $\alpha$ and $t$. The geometric interpretation of a fractional integral is, therefore, non-static as it depends on the value of both $\alpha$ and $t$.

@@

\begin{abstract}
Having geometrical ideas  interpretations of complex mathematical ideas is crucial if we
An abstract should not contain concrete mathematics, but rather should be discrete.  Be brief and avoid using mathematical notation except where absolutely necessary, since this brief synopsis will be used by search engines to identify your article!
\end{abstract}

>>>>

\title{Visualization of the Riemann-Liouville Fractional Integral}
\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
%\author{ }

@@

%To conclude this section, a fractional integral of order $\alpha$ and extent $t$ can be interpreted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose 
%shape is determined by $\alpha$ and $t$. The geometric interpretation of a fractional integral is, therefore, non-static as it depends on the value of both $\alpha$ and $t$.

@@

\begin{abstract}
In this paper we present a novel geometric interpetation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the 
order of integration $\alpha$ and the integration limit $t$. We also emphasize the pedagogical benefits that this interpretation offers, as it is very 
similar in nature to the geometric interpretation that is associated with classic Riemann integrals.   
\end{abstract}
